\documentclass[11pt,a4paper]{article}
\usepackage{fontspec}
\setmainfont{Adobe 宋体 Std L}
\begin{document}
世界,你好!chinese
a park a yard a region a bench kindergarten playground

to come to take to plant to dig to leave to live

a child a neighbor neighbors a kindergarten teacher

The women are neighbors.

This woman is our neighbor.

quiet a loud yard a quiet region loud a quiet yard a loud region

A small park next to the building.

a loud playground in a yard.

a quiet yard in a small region

a loud region in a big city.

a quiet yard in a small city.

a quiet park in a loud region.

Neighbors live next door.

The neighbors are going for a walk with their children in the playground.

The neighbors are sitting on a bench in the yard.

These neighbors live in small homes.

The husband and wife are meeting their neighbors in the park.

These neighbors live in a big, loud building.

The kindergarten teacher in the kindergarten is reading the children a book.

The kindergarten teacher takes the children on a walk.

The father is takeing his children to the playground.

The mother takes her children to kindergarten.

Children are playing with the kindergarten teacher.

The kindergarten teacher is taking the children from the playground to the
kindergarten.

In the summer the family leaves to the south.

The woman comes to a quiet region to live.

People don't want to live in this region: Here there isn't a kindergarten.

The family leaves for vacation.

The children don't want to leave this region - here there's a big playground.

People come to this quiet park to go for a walk and relax.

The daughter is helping her mother plant flowers.

The mother is planting flowers in the small garden next to the house.

In the spring the neighbors dig up earth in the park.

The excavator is digging up earth in the yard.

Children dig in the sand in the playground.

They plant trees and flowers in their region.

From where do people come to the big park?

People come from loud regions of the city.

Where do the tourists come from? They come from different cities.

Where do parents take children? Parents take children to the playground.

Where are the neighbors coming from? They're coming from a store.

Where does the kindergarten teacher take children? She takes them to the
kindergarten.

Where does the family leave in the winter? In the winter the family leaves to
the south.

Why are the children digging in the sand? They're building a sandcastle.

Where do children dig in the sand? They dig in the sand in a playground.

Why are people digging up earth? They want to plant a tree in the park.

Why is the woman digging up earth in front of her house? She's planting flowers
there.

Where do they plant flowers? They plant flowers in the park.

Where are the women talking? They're talking on a bench in the park.


\end{document}
